\racets: Policy{-}Agnostic Programming in Racket

### 2018-07-24 paper/paper.tex
small tweaks
nit

To handle this, we implement a macro for the \code{lambda} form, to
tag Racet closures specifically (so that they are differentiated from
functions outside of the current module). In the case that a foreign
function is applied to a faceted value, our implementation of function
application wraps the function to be able to handle facets by
distributing the function through each branch of the facet.

@@

>>>>

To handle this, we implement a macro for the \code{lambda} form, to
tag \racets closures specifically (so that they are differentiated from
functions outside of the current module). In the case that a foreign
function is applied to a faceted value, our implementation of function
application wraps the function to be able to handle facets by
distributing the function through each branch of the facet.

@@

Our implementation is currently available on Github at
\blue{\url{https://github.com/fordsec/racets}}
